Modelling the emergence of whisker barrels

### 2020-06-16 paper/briefpaper/brief.tex
Merging one small conflict

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}, \cmnt{Fig.\,5b}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from \stu{the}
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \stu{provide a} measure \cmnt{of} the correspondence
      between the real and simulated barrel shapes, $\eta$ (the sum of differences in
      area; units \cmnt{mm$^2$});
      \cmnt{grey hexagons \stu{provide a measure of how selectively each cortical site is innervated}, $\omega = \oiint_{S} \left( \mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i\right) \mathrm{d}S$. }
      \textbf{E} \stu{Plotted across the cortical sheet, the selectivity develops to reveal an alignment with the emergent barrel boundary shapes}
      \cmnt{The colour map indicates the values of  $\mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i(c_i)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=113.5\,(1.2)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=115\,(1.9)$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=114.31$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

@@

\cmnt{The pattern-matching metric, $\eta$, incorporates information about i)
  the differences in the areas of the simulated and experimental barrels
  ($\mathcal{A}_i^{\mathrm{sim}}$ and $\mathcal{A}_i^{\mathrm{exp}}$); and ii)
  the information provided by `adjacency vectors', $\mathcal{V}_i$ (one for
  each barrel) whose $N$ elements contain the length of the barrel boundary
  which adjoins each other barrel in the pattern. The value of
  $\mathcal{V}_{i,j}$ (the $j^{\mathrm{th}}$ element of $\mathcal{V}_i$) is
  the length of the boundaries between regions of type $i$ and regions of type
  $j$. In a well-formed barrel pattern, $\mathcal{V}_{i}$ is a sparse vector
  and note that $\mathcal{V}_{i,i} = 0, \forall i$. $\mathcal{V}_{i}$ can be
  computed for the experimental and simulated barrel patterns and compared. A
  dimensionless measure of the pattern's arrangement and neighbour relations
  can be obtained from the scalar product of the simulated and experimental
  adjacency vectors:
  $\frac{1}{N} \sum_i \frac { \mathcal{V}_{i}^{\mathrm{sim}}}
  {b_{i}^{\mathrm{sim}} } \vcdot \frac{\mathcal{V}_{i}^{\mathrm{exp}}}{b_{i}^{\mathrm{exp}}}$, where
  $b_i^{\mathrm{exp}}$($b_i^{\mathrm{sim}}$) is the total length of the boundary of
  experimental(simulated) barrel $i$. This measure is low early in the simulation, when the regions do
  not have the neighbour relations of the experimental pattern
  (Fig.\,\ref{fig:main}C, $t=1000$) and maximal when the neighbour relations
  have become established ($t=10000$). It does not distinguish between
  $t=10000$ and $t=30000$.}
%
\cmnt{A second way to analyse the adjacency vectors is to consider
  the mean magnitude of the difference between the simulated and experimental
  vectors: $\frac{1}{N} \sum_i \norm{ \mathcal{V}_{i}^{\mathrm{sim}} -
    \mathcal{V}_{i}^{\mathrm{exp}} } $. This tends to 0 for a perfect
  match and can separate patterns with straight boundaries from those with
  noise on the boundary shape (For an example of `noisy edges', see Fig.\,\ref{fig:sens}B.ii).}
%
\cmnt{We combined all of these measures into a single pattern quality metric:}
%
\begin{equation} \label{eq:eta}
\color{blue}
  \eta =
  \frac
  {
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{A}_i^{\mathrm{sim}} - \mathcal{A}_i^{\mathrm{exp}} }
    \times
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{V}_{i}^{\mathrm{sim}} -
      \mathcal{V}_{i}^{\mathrm{exp}} }
  }
  {
    \frac{1}{N}
    \sum_i \frac {\mathcal{V}_{i}^{\mathrm{sim}}} {b_{i}^{\mathrm{sim}}}
    \vcdot
    \frac {\mathcal{V}_{i}^{\mathrm{exp}}} {b_{i}^{\mathrm{exp}}}
  }
\color{black}
\end{equation}
%
\cmnt{which has units of mm$^3$.}

>>>>

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}, \cmnt{Fig.\,5b}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from \stu{the}
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \cmnt{give a} measure \cmnt{of} the correspondence
      between the real and
      simulated barrel shapes, $\eta$ (the \cmnt{pattern quality metric---see
        Materials \& Methods; units mm$^3$});
      \cmnt{grey hexagons \stu{provide a measure of how selectively each
          cortical site is innervated} OR: show the measure of localization, $\omega =
        \oiint_{S} \left( \mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i\right) \mathrm{d}S$. }
      \textbf{E} \stu{Plotted across the cortical sheet, the selectivity
        develops to reveal an alignment with the emergent barrel boundary
        shapes} OR: \cmnt{The localization measure plotted across the domain
        shows that the structure in the connection density which has developed
        by $t=30000$ is largely absent at $t=1000$. The
        colour map
        indicates the values of  $\mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i(c_i)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=113.5\textbf{!!}\,(1.2)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=115\,(1.9)\textbf{!!}$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06\textbf{!!}$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=114.31\textbf{!!}$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

@@

\cmnt{The pattern-matching metric, $\eta$, incorporates information about i)
  the differences in the areas of the simulated and experimental barrels
  ($\mathcal{A}_i^{\mathrm{sim}}$ and $\mathcal{A}_i^{\mathrm{exp}}$); and ii)
  the information provided by `adjacency vectors', $\mathcal{V}_i$ (one for
  each barrel) whose $N$ elements contain the length of the barrel boundary
  which adjoins each other barrel in the pattern. The value of
  $\mathcal{V}_{i,j}$ (the $j^{\mathrm{th}}$ element of $\mathcal{V}_i$) is
  the length of the boundaries between regions of type $i$ and regions of type
  $j$. In a well-formed barrel pattern, $\mathcal{V}_{i}$ is a sparse vector
  and note that $\mathcal{V}_{i,i} = 0, \forall i$. $\mathcal{V}_{i}$ can be
  computed for the experimental and simulated barrel patterns and compared. A
  dimensionless measure of the pattern's arrangement and neighbour relations
  can be obtained from the scalar product of the simulated and experimental
  adjacency vectors:
  $\frac{1}{N} \sum_i \frac { \mathcal{V}_{i}^{\mathrm{sim}}}
  {b_{i}^{\mathrm{sim}} } \vcdot \frac{\mathcal{V}_{i}^{\mathrm{exp}}}{b_{i}^{\mathrm{exp}}}$, where
  $b_i^{\mathrm{exp}}$($b_i^{\mathrm{sim}}$) is the total length of the boundary of
  experimental(simulated) barrel $i$. This measure is low early in the simulation, when the regions do
  not have the neighbour relations of the experimental pattern
  (Fig.\,\ref{fig:main}C, $t=1000$) and maximal when the neighbour relations
  have become established ($t=10000$). It does not distinguish between
  $t=10000$ and $t=30000$.}
%
\cmnt{A second way to analyse the adjacency vectors is to consider
  the mean magnitude of the difference between the simulated and experimental
  vectors: $\frac{1}{N} \sum_i \norm{ \mathcal{V}_{i}^{\mathrm{sim}} -
    \mathcal{V}_{i}^{\mathrm{exp}} } $. This tends to 0 for a perfect
  match and can separate patterns with straight boundaries from those with
  noise on the boundary shape (For an example of `noisy edges', see Fig.\,\ref{fig:sens}B.ii).}
%
\cmnt{We combined all of these measures into a single pattern quality metric:}
%
\begin{equation} \label{eq:eta}
\color{blue}
  \eta =
  \frac
  {
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{A}_i^{\mathrm{sim}} - \mathcal{A}_i^{\mathrm{exp}} }
    \times
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{V}_{i}^{\mathrm{sim}} -
      \mathcal{V}_{i}^{\mathrm{exp}} }
  }
  {
    \frac{1}{N}
    \sum_i \frac {\mathcal{V}_{i}^{\mathrm{sim}}} {b_{i}^{\mathrm{sim}}}
    \vcdot
    \frac {\mathcal{V}_{i}^{\mathrm{exp}}} {b_{i}^{\mathrm{exp}}}
  },
\color{black}
\end{equation}
%
\cmnt{which has units of mm$^3$.}
